\documentclass[a4paper, 12pt]{scrartcl}
\usepackage{amsmath,amsfonts}
\usepackage{scrpage2}
\usepackage{scrtime}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{verbatim}
%\usepackage{harvard}
\usepackage{color}
\usepackage{url}
\usepackage[margin=1in]{geometry}

\pagestyle{scrheadings}
\setlength\headheight{25.2pt}
%\chead{\thepage}
\ohead{DUC TAM, HOANG}
\ihead{Statement Of Purpose}
\setheadsepline[head]{3pt}
\renewcommand{\headfont}{\normalfont}
\newcommand{\sqz}{\hfill\phantom{.}}
\newcommand{\thickhline}{\noalign{\hrule height 0.8pt}}
\renewcommand{\baselinestretch}{1.1} 
\setlength\parindent{0mm}
\setlength\parskip{5mm}

\begin{document}

%%%%%%%%%%%%%%%%%%% START %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

I have studied and worked on computational linguistics for quite some times. 
There is a glooming fear among the Natural Language Processing (NLP) community that nowadays people can solve NLP problem without any linguistic knowledge, i.e. word embeddings.
On the other hand, linguistic knowledge is sometimes important in other fields, such as data mining or computer vision, because natural language text is part of any ``big data''. 
I rather see this phenomenon as a positive trend. 
In fact, I am interested in the opportunity that I can work in a various fields with my background of mathematics, machine learning and linguistics. 


% Talking about the master thesis
Instead of a formal introduction of my research interests, I offer a summary of my master thesis, which earned me excellent score at Charles University in Prague. 
The thesis was carried out in 12 months under supervision of Dr. Ondrej Bojar (without course works), providing me an insight into the life of a PhD student.
Working with Dr. Bojar was indeed a motivation for me to develop myself more. I grew more and more interested in computational linguistics in general. 
He gave me the full freedom to propose my plan, implement necessary tools, conduct experiments and write report while simultaneously giving me advices and monitoring my project. 

We approached the problem of statistical machine translation between Czech and Vietnamese, which had been proved to be difficult, and no one had ever worked on it.
After discussing, we decided to alleviate the problem by pivoting, i.e using a third language. 
The project offered a realistic condition that we had to prepare our own training data, test data and implementation.
Sometimes, I could not help feeling overwhelmed with the huge amount of work as we started from scratch.
The project taught me how to maintain a schedule in a long period, especially when some experiments failed.



%%%%%%%%%%%% A year off #########################
After graduation, I remained wary about commiting myself prematurely to a PhD program or a specific research topic. 
I opted to take a gap year away from school, hoping to gain some perspective, work on a different topic and strengthen my background before embarking on a long period of PhD.
I applied and became a research assistant at the National University of Singapore, which is a bit closer to my home.
I moved to Singapore to work under supervision of Professor Hwee Tou Ng.  


Upon joining Prof. Ng's research group. I was assigned the task of grammatical error correction.
After discussion, we agreed to focus on the statistical machine translation approach, i.e. building a system to translate bad English to good English. 
I devised a method to post-process the output of standard SMT systems, resulting in a significant improvement ($p\mbox{-}value < 0.01$) over a state-of-the-art baseline. 
I subsequently wrote a paper (as first author) on these results and submited it to the IJCAI 2016.  

%%%%%%%%%%%%%%% Why I am good for you ########################
Time being a research assistant allows me to reread my past research project from a more critical stance. It also gives me sufficient time to search and research for doctorate program that best suit my needs.
University of Edinbergn is always in my mind. Not only it is home to the famous Moses system that I have been using for statistical machine translation, it has an outstanding record of research.

Though I cannot predict how different the environment there is from my past experience, I believe that I can adapt to the new environment. 
My past experience has taught me that I am no genius, but I cane get things done through hard work.
It took me a month to cope with and thrive at Charles University in Prague.
It took me much less time to familiarise with the research environment here in Singapore.
I believe that I can do it again. 



\newpage
%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
I love research, leaning a bit towards applied research.
I like to solve specific questions that help humanity. 
I like to cope up with new and challenging tasks.
I like the flexible working hours
 

I started working 





Rather than working on one topic for my whole life, I was trying to be a generist. 
It was the reason I keep bounching from one place to another. I start my career 

%Talk about your relevant experience
I have been a lab rat for years. 
Some people ask me whether I love doing research. Honestly, I can't answer. 
Years of being a lab rat help me familiarise with the .
After years of studying and doing research, I believe that I have learned a thing or two about doing research. 




I see myself as a lab rat, who keeps bouncing from one place to another. And now, I believe that it is the high time the rat need to settle down and do a PhD.



Instead of a formal introduction of my research interests, I offer a summary of my master thesis, which earned me excellent score at Charles University in Prague. 
We approached the problem of Czech-Vietnamese machine translation, which had been proved to be difficult, yet interesting.
After discussing with my advisor, we decided to alleviate the problem by pivoting, i.e using a third language. 
I start the project by searching and reading related papers simultaneously banging my head against the wall of 

Working with Dr. Bojar was indeed a motivation for me to develop myself more. I grew more and more interested in computational linguistics in general. 



I did make a mistake when overlooking the potential of an easy yet useful approach, loosing an opportunity to graduate early. 


I have spent one year doing my master thesis under supervision of Dr. Bojar. 
We aimed to build a machine translation system between Czech and Vietnamese, two distinctive languages of two families. 
Our approach was that of the pivoting methods.
Pivoting method is an alternative method to do machine translation with the help of a third language. 
Because it was my thesis, I carried out most of the works. They include making schedule, reading papers, choosing technology, designing experiments and programming.
My supervisor was so helpful. 
He was the one who approved my suggestion, gave me meaningul advice and helped me when I ran into trouble. 




I leave UFAL to become a research assistant. 
It was an odd choice for me to take a gap year.
I want to strengthen my background before continueing with a PhD program. 


%Talking about your personal life story vs. your professional background




%Why is it good for the university
I always see myself as the one who get things done through hard work. 
When I joined the master program at Charles University, I was by no mean the brightest guy. 
I had a mixed background with no solid, 
However, I work hard enough to 
Finally, I was one of a few students who manage to finish the program on time. 
I had one publication with an excellent GPA. 

I believe that I can get the job done if I am accepted to your program.

The letter is rather formal, if you are interested in seeing who I am, please take a look at my personal page: \url{http://tamhd.github.io}. The page is a free distribution of github that I take advantage. 

\end{document}

